### 2020-01-01 methods.tex
added methods section

The exponent $\alpha$ is the power law exponent that arise in our \emph{Theory of Heavy Tailed Self Regularization}, and is the determined by fitting the Empirical Spectral Density (ESD) of $\mathbf{X}$--i.e. a histogram of the eigenvalues--$\rho(\lambda)$ to a truncated power law

>>>>

The exponent $\alpha$ is the power law exponent that arises in our \emph{Theory of Heavy Tailed Self Regularization}, and is the determined by fitting the Empirical Spectral Density (ESD) of $\mathbf{X}$--i.e. a histogram of the eigenvalues--$\rho(\lambda)$ to a truncated power law
